\section{Lec 15}

As another example of Lemma \ref{lem15}, consider $\widetilde{B}_n$:
\[
    C = \begin{pmatrix}
        2 & -\sqrt{2} &  & \\
        -\sqrt{2} & 2 & -1 & \\
         & -1 & 2 & \ddots & \\
         & & \ddots & \ddots & -1 & -1 \\
         & & & -1 & 2 & 0 \\
         & & & -1 & 0 & 2
    \end{pmatrix}
\]
The following linear combination of rows is zero:
\[
    \sqrt{2} R_1 + 2 R_2 + 2 R_3 + \dots + 2 R_{n-1} + R_n + R_{n+1} = (0, 0, \dots, 0),
\]
so $\det C = 0$.

{\bf Definition}: By a {\em subgraph} of a Coxeter graph $G$, we mean a graph
obtained from $G$ by successively removing vertices (and the corresponding
incident edges), and/or lowering labels, (including changing $m>2$ to $m=2$,
hence removing an edge).

% TODO examples

\begin{proposition} \label{prop16}
Let $G$ be a positive definite graph. Then all of its subgraphs are positive
definite.
\end{proposition}

(We don't consider the empty subgraph)

\begin{proof}
Every subgraph $G'$ is obtained by successively removing vertices and/or
lowering labels of $G$. Hence it suffices to consider the following two cases:
\begin{enumerate}
\item[(1)] $G'$ obtained from $G$ by removing a single vertex.
\item[(2)] $G'$ obtained from $G$ by lowering a single label.
\end{enumerate}

In case (2), assume we lower label $m_{kl}$ to $m'_{kl}$, where
$2 \leq m'_{kl} < m_{kl}$. Then $C_{ij} = C'_{ij}$ unless $(i,j)=(k,l)$ or
$(i,j)=(l,k)$, and $C_{kl} = C_{lk} < C'_{kl} = C'_{lk}$. By contradiction,
assume there exists a nonzero $x \in \R^r$ such that
\[
    \sum_{i,j} x_i C'_{ij} x_j \leq 0.
\]
Let $y := (|x_1|, \dots, |x_r|)$. Then, by the positive definiteness of $C$,
\begin{align*}
    0 &< \sum_{i,j} y_i C_{ij} y_j \\
    &= \sum_{i,j} y_i C'_{ij} y_j +
    \underbrace{2( \underbrace{C'_{kl} - C'_{lk}}_{<0}) y_k y_l}_{\leq 0} \\
    &\leq \sum_{i,j} y_i C'_{ij} y_j \\
    &= 2 \sum_{i} y_i^2 +
    \underbrace{\sum_{i \neq j} y_i \underbrace{C'_{i,j}}_{\leq 0} y_j}_{\leq 0} \\
    &\leq 2 \sum_{i} x_i^2 +
    \sum_{i \neq j} x_i C'_{i,j} x_j \\
    &= \sum_{i,j} x_i C'_{i,j} x_j
\end{align*}

In case (1), assume WLOG we have deleted the vertex labelled $r$. Then,
$C'$ follows from $C$ by removing the $r^{\text{th}}$ (last) row and column.
Hence $C'$ is positive definite (it is one of the principal minors of $C$).
\end{proof}

\begin{proposition} \label{prop17}
The only potential Coxeter graphs corresponding to finite reflection groups are
the following.
\end{proposition}

% TODO draw graphs

That is, we will show that any graph not in this list must have one of the
graphs from Lemma \ref{lem15} as a subgraph. It will remain to show that these
graphs are indeed positive definite.

\begin{proof}
Because $\widetilde{D}_n$ is not an admissible subgraph, we can have at most
one branch point (vertex of degree $>2$).
Because $\widetilde{A}_{n-1}$ is not admissible, we cannot have cycles or
$\infty$ labels.

This leaves us with only two types of graphs: linear chains, and graphs with
a single branch point.

We continue the proof in the next lecture.
\end{proof}
